Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}

### 2017-08-18 revision/review_response.tex

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage{lineno}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage{paralist}
\usepackage{bm}
\usepackage{fixltx2e}

@@

\Bigtxt{Reviewer 1:}

The authors present the sensitivity analysis of a 0-Dimensional biochemical model implemented in Weeks Bay Alabama. The authors evaluated the sensitivity of the model predictions of DO, ammonium, nitrate, chl-a and irradiance to perturbations in several model parameters. In general, the theoretical basis of the sensitivity analysis is very interesting and mathematically sound and the use of the collinearity index (Eq. 3) to explore linear correlations between parameters seems to be very useful to help identify the most important parameters controlling the model performance (in terms of goodness of fit to observed datasets). The paper can be accepted pending major revisions.

My main concern with the manuscript is that while the application of the sensitivity analysis to the FishTank model seems ok, the application of the FishTank model to Weeks Bay, AL is weak and not convincing. First of all, a correct representation of the advective and dispersive transport is critical to be able to capture the fate and transport of water quality in an estuary. Without a correct representation of transport it is almost impossible to be able to obtain a predictive water quality model. The FishTank model in this case neglects all modes of transport in Weeks Bay, AL and therefore assume the estuary is like a bathtub. This is obviously incorrect and represents a clear limitation of the paper.

{\it

We agree with the reviewer that this application is not entirely appropriate given the hydrodynamic influences on the observed data. However, our objective was to demonstrate that unit-testing of the zero-dimensional is an efficient means of improving larger models that are computationally intensive.  Our intent was not to present a complete predictive model with hydrodynamic forcing to Weeks Bay. To address the concern of the reviewer and to maintain our emphasis on unit-testing, we have chosen a a more appropriate dataset, described below.  A sentence added to the final paragraph of the introduction emphasizes our intent of the analysis:

'In general, the analysis makes a case for unit-testing with lower-dimensional models, particularly when computional limitations preclude the use of conventional optimization algorithms with larger three-dimensional models.'

An alternative dataset was used that included flask experiments of oxygen production from Pensacola Bay, Florida.  This dataset included light and dark treatments of water samples in closed bottles for an approximate 12-hour period, including before and after measurements of DO concentrations with initial nutrient values for each treatment and replicate.  The dataset is described in detail in Murrell et al. in revision (Murrell, M. C., Caffrey, J. C., Marcovich, D. T., Beck, M. W., Jarvis, B. M., III, J. D. H., in revision. Seasonal oxygen dynamics in a warm temperate estuary: Effects of hydrologic variability on measurements of primary production, respiration, and net metabolism. Estuaries Coasts - (-), –.).  Methods were added to the manuscript, Sec. 2.4:

`Estimates of oxygen production from closed bottle experiments were used to calibrate the 0-D model.  Surface water was collected from a fixed location in Pensacola Bay, Florida (30.35$^{\circ}$ N, 87.20$^{\circ}$ W) on September 25\textsuperscript{th}, 2013 (full details in Murrell et al. in revision).  Water samples were placed into closed 300 mL glass bottles and transported back to the lab for treatments.  Concentrations of O$_2$ and nutrients (NH$_4^+$, NO$_2^-$, NO$_3^-$, PO$_4^{3-}$, and SiO$_3^{2-}$) were extracted from the samples within one hour of collection. Oxygen concentrations were established using Winkler reagents (Parsons et al. 1985) and titration using a MetrOhm Titrando with thiosulfate titrant calibrated against an iodate standard and electrochemical endpoint detection.  Ammonium was analyzed using a fluorometric method (Holmes et al. 1999); other nutrients were analyzed using either a Thermo Fisher Aquakem 200 discrete analyzer or an Astoria-Pacific continuous flow analyzer using standard colorimetric methods (APHA 2005).

Oxygen production after an approximate 12 hour period (morning to evening) was estimated within the bottles using light and dark treaments.  All treatments were exposed to ambient outdoor conditions in a water bath at the laboratory.  The dark treatments used opaque black bottles to ensure no exposure of ambient light to the samples.  The exposure experiments began at 7am and were concluded at 7pm, after which the concentrations of O$_2$ in each bottle were measured.  Each treatment had four replicates and HOBO\textsuperscript{\textregistered} pendants were used to measure continuous temperature and light. Starting O$_2$ concentrations for the experiments were $200.78$ ($\pm$ $4.47$) mmol O$_2$ m$^{-3}$ and ending concentrations were $229.57$ ($\pm$ $2.66$) mmol O$_2$ m$^{-3}$ for the light treatments and $195.51$ ($\pm$ $1.9$) mmol O$_2$ m$^{-3}$ for the dark treatments.  Initial nutrient concentrations were $0.71$ mmol m$^{-3}$ for NH$_4^+$ (single sample), $0.13$ mmol m$^{-3}$ for PO$_4^{3-}$, and $38.4$ mmol m$^{-3}$ for SiO$_3^{2-}$. Concentrations for NO$_2^-$ and NO$_3^-$ were below detection limit.

Each parameter subset for O$_2$ from the selection heuristics was calibrated to the ending oxygen concentration for each of the four replicates of each treatment. The intial nutrient and oxygen concentrations were used as starting conditions for FishTank.  The corresponding continuous temperature and light measurements were also used as forcing conditions.  Parameter values were searched using the optim function...
'
}
